Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-08 robdml.tex
tex

>>>>

In literature, a series of triplet sampling strategies exist, such as random,
semi-hard~\cite{facenet}, soft-hard[], distance[], and hardest sampling.
%
Any of these can be selected for source triplet and destination triplet.

As the samples will not become adversarial once $H_S>H_D$ (zero perturbation in
this case according to \cref{eq:hm}, an effective combination of source and
destination sampling strategy should make the expectation of source hardness
less than the source hardness, \ie, $E[H_S]<E[H_D]$.
%
Our empirical observation on $E[H]$ from randomly initialized
model suggests a sorting of ``random'' $<$ ``semi-hard'' $<$ ``soft-hard'' $<$
``distance'' $<$ ``hardest''.
%
Namely, the source sampling strategy should be ahead of the destination
sampling strategy in this list.
